Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-02-06 WSSSPE3/report/wg_appendix_software_credit.tex
added missing possessive s

\item Mozilla Science Lab' recently introduced Contributorship Badges for
Science~\cite{Mozilla_badges}, which provide a badge---associated with an
ORCID~\cite{orcid}---that recognizes author contributions using the taxonomy
outlined in Project CRediT.

>>>>

\item Mozilla Science Lab's recently introduced Contributorship Badges for
Science~\cite{Mozilla_badges}, which provide a badge---associated with an
ORCID~\cite{orcid}---that recognizes author contributions using the taxonomy
outlined in Project CRediT.
